---
title: "Telecommunications Marketing Survey Report"
author: "Melissa Wu"
date: "July 11, 2023"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, comment="", warning = FALSE, message = FALSE, tidy.opts=list(width.cutoff=55), tidy = TRUE)
```

```{r libraries}
library(data.table)
library(DT)
```

```{r source}
source("constants.R")
source("functions.R")
```

```{r read_data}
# Set Working Directory to Source File Location
mobile = fread(input ="../Data/mobile_phone_survey_data.csv")
```

```{r define}
mobile$`Age Group` <- cut(mobile$Age, breaks = unlist(age_groups), labels = age_labels)
mobile$`Income Group` <- cut(mobile$Income, breaks = unlist(income_groups), labels = income_labels)
```

```{r functions}
```




# Calculations {.tabset}


### Q1: Respondent Variables {.tabset}

#### Age Group
  
What are the distribution of respondents across **age groups**?  
  
```{r q1_age.group}
datatable(respondent(mobile, age.group.name))
```

#### Gender
  
What are the distribution of respondents across **gender**?   

```{r q1_gender}
datatable(respondent(mobile, gender.name))
```

#### Income Group
  
What are the distribution of respondents across **income groups**?   
  
```{r q1_income.group}
datatable(respondent(mobile, income.group.name))
```

#### Region
  
What are the distribution of respondents across **region**?   
  
```{r region}
datatable(respondent(mobile, region.name))
```

#### Persona
  
What are the distribution of respondents across **persona**?  
  
```{r persona}
datatable(respondent(mobile, persona.name))
```


### Q2:  Segmented Outcomes {.tabset}

#### Part A

What are the top 5 products by Awareness rates in the Northeast?

```{r q2_a}
eng1 <- engagement(mobile, awareness.name, age_labels, gender_labels, income_labels, "Northeast", persona_labels, 5)
datatable(eng1)

```

#### Part B

What are the top 5 products by advocacy rates among female respondents who earn at least $100,000?

```{r q2_b}
eng2 <- engagement(mobile, advocacy.name, age_labels, "Female", c("100,000 - Under 150,000", "150,000+"), region_labels, persona_labels, 5)
datatable(eng2)
```





### Q3:  Overall Brand Perceptions {.tabset}

What are the top 5 brands by the overall average perception?


```{r q3}
top5.ave.perception <- brand.percept(mobile, age_labels, gender_labels, income_labels, region_labels, persona_labels, 5)
datatable(top5.ave.perception)
```


### Q4: Gaps in Outcomes {.tabset}


#### Part A

Which 5 products have the largest gap between the rate of consumption and the rate of awareness?  This would correspond to a formula of Difference = 100 * (Average Consumption - Average Awareness).  (Please use this exact formula.  Do not use the absolute value.  Focus only on the highest positive gaps.)  Display a bar graph showing the 5 largest differences in decreasing sorted order.

```{r q4_a}
outcome1 <- outcome.gap(mobile, consumption.name, awareness.name, 5, 2)

ggplot(data=outcome1, aes(x=reorder(Product, -Difference), y=Difference)) +
  geom_bar(stat="identity", width=0.5, fill="steelblue") + xlab("Product")


```
  
  
#### Part B

Which 5 products have the largest gap between the rate of awareness and the average satisfaction?  This would correspond to a formula of Difference = 100 * (Average Awareness - Average Satisfaction).  (Please use this exact formula.  Do not use the absolute value.  Focus only on the highest positive gaps.)  Display a bar graph showing the 5 largest differences in decreasing sorted order.

```{r q4_b}
outcome2 <- outcome.gap(mobile, awareness.name, satisfaction.name, 5, 2)

ggplot(data=outcome2, aes(x=reorder(Product, -Difference), y=Difference)) +
  geom_bar(stat="identity", width=0.5, fill="steelblue") + xlab("Product")

```
  


### Q5: Aggregated Engagement {.tabset}

#### Part A

How much impact does respondent's overall trends in awareness have for that person's awareness with Buzzdial phones?

```{r q5_a}
ag.engage(mobile, awareness.name, "Buzzdial", age_labels, gender_labels, income_labels, region_labels, persona_labels)

```

#### Part B

How much impact does respondent's overall trends in satisfaction have for that person's satisfaction with Buzzdial phones?

```{r q5_b}
ag.engage(mobile, satisfaction.name, "Buzzdial", age_labels, gender_labels, income_labels, region_labels, persona_labels)

```

