---
title: "Mobile Phones"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
runtime: shiny
---


```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(rmarkdown)
library(knitr)
library(Hmisc)
library(DT)

library(data.table)
assignInNamespace("cedta.override", c(data.table:::cedta.override,"rmarkdown"), "data.table")

opts_chunk$set(echo = FALSE, comment="", warning = FALSE, message = FALSE, tidy.opts=list(width.cutoff=55), tidy = TRUE)

```

```{r source_functions}
source("constants.R")
source("functions.R")
```

```{r read_data, include=FALSE, eval=TRUE}
# Read the file from relevant directory on your local computer
# /Users/apple/Downloads/AA5902_DataScienceConsulting/IndProj3

mobile <- fread(input = "../Data/mobile_phone_survey_data.csv", verbose = F)

```

```{r constants}
# Most constants have been placed in the file constants.R to unify the work across reporting and applications.
# Additional constants that are unique to this reporting engine can be added here.

### add age group column & income group columns
age_groups <-  c(17, 34, 49, 64, 75)
age_labels <- c('18-34', '35-49', '50-64', '65+')

income_groups <- c(-1, 49999, 69999, 99999, 149999, Inf)
income_labels <- c('Under 50,000', '50,000 - Under 75,000', '75,000 - Under 100,000', '100,000 - Under 150,000', '150,000+')

mobile$`Age Group` <- cut(mobile$Age, breaks = unlist(age_groups), labels = age_labels)
mobile$`Income Group` <- cut(mobile$Income, breaks = unlist(income_groups), labels = income_labels)

# unique variables
unique.age.groups <- mobile[, sort(unique(get(age.group.name)))]
unique.genders <- mobile[, sort(unique(get(gender.name)))]
unique.income.groups <- mobile[, sort(unique(get(income.group.name)))]
unique.regions <- mobile[, sort(unique(get(region.name)))]
unique.personas <- mobile[, sort(unique(get(persona.name)))]

unique.products <- mobile[, unique(get(product.name))]

respondent.variables <- c(age.group.name, gender.name, income.group.name, region.name, persona.name)
states.of.engagement <- c(awareness.name, consideration.name, consumption.name, satisfaction.name, advocacy.name)

bp.traits <- names(mobile)[grep(pattern = bp.pattern, x = names(mobile))]


```


```{r functions}
# Most functions have been placed in the file functions.R to unify the work across reporting and applications.

# Additional functions that are unique to this reporting engine can be added here.
```





Introduction
=====================================  

We are analyzing data from the Marketing Department examining respondents' engagement and perception on telecommunication products.  

The survey was given to `r mobile[, length(unique(get(id.name)))]` respondents and covered `r mobile[, length(unique(get(product.name)))]` separate products.

Click on the tabs to see different reports.




Respondents
===================================


Row {data-height=500}
-------------------------------------

```{r q1_input}
inputPanel(
  selectInput(inputId="respondent_variable", label = "Select Variable:", choices = respondent.variables, selected = respondent.variables[1]),
)
```

Row {data-height=500}
-------------------------------------

```{r q1_output}
renderPlot({
  tab <- percentage.table(x = mobile[, .SD[1], by = id.name][, get(input$respondent_variable)])
  barplot(height = tab, space=0.01, las = 1, main = input$respondent_variable, ylab = "Percentage", xlab = input$respondent_variable, ylim = c(0, 1.2*max(tab, na.rm = TRUE)), col = "dodgerblue")
  
  space_val = 0
    text(x = -0.4 + 1:length(tab) * (1+space_val), y = tab, labels = sprintf("%.1f%%", tab), pos = 3)
})
```

Engagement
=====================================  


Row {data-height=500}
-------------------------------------

```{r q2_input}
inputPanel(
  selectInput(inputId="em_state", label = "State of Engagement:", choices = states.of.engagement, selected = states.of.engagement[1]),
  selectInput(inputId="em_inputs", label = "Choose Inputs:", choices = c(age.group.name, gender.name, region.name, income.group.name, persona.name), selected = c(age.group.name, gender.name, region.name, income.group.name), multiple = TRUE),
  selectInput(inputId="em_age_group", label = "Age", choices = unique.age.groups, selected = unique.age.groups, multiple = TRUE),
  selectInput(inputId = "em_gender", label = "Gender", choices = unique.genders, selected = unique.genders, multiple = TRUE),
  selectInput(inputId = "em_income_group", label = "Income", choices = unique.income.groups, selected = unique.income.groups, multiple = TRUE),
  selectInput(inputId = "em_region", label = "Region", choices = unique.regions, selected = unique.regions, multiple = TRUE),
  selectInput(inputId = "em_persona", label = "Persona", choices = unique.personas, selected = unique.personas, multiple = TRUE),
  sliderInput(inputId = "em_number_of_products", label = "Number of Top Products", min = 0, max = 20, value = 5, step = 1)
)
```

Row {data-height=800}
-------------------------------------

```{r q2_output}
renderPlot({
  tab <- mobile[get(age.group.name) %in% input$em_age_group & get(gender.name) %in% input$em_gender & 
                get(income.group.name) %in% input$em_income_group & get(region.name) %in% input$em_region & 
                get(persona.name) %in% input$em_persona][, .(Mean = round.numerics(100*mean(get(input$em_state), na.rm=TRUE), 2)), by = product.name]
  setorderv(x = tab, cols = "Mean", order = -1)
  topk.engage <- tab[1:input$em_number_of_products]
  
  barplot(height = topk.engage[,Mean], names.arg = topk.engage[ ,get(product.name)], space=0.01, las = 1, ylab = sprintf("Rate of %s", input$em_state), ylim = c(-10, 100), axes = F, col = "dodgerblue")
  axis(side = 2, at = 20*(0:5), las = 2)
  
    space_val = 0
    text(x = -0.4 + 1:topk.engage[,.N] * (1+space_val), y = topk.engage[, Mean], labels = sprintf("%.1f%%", topk.engage[, Mean]), pos = 3)
})
```


Brand Perception
=====================================  

Row {data-height=800}
-------------------------------------

```{r q3_input}
inputPanel(
  selectInput(inputId="bp_age_group", label = "Age", choices = unique.age.groups, selected = unique.age.groups, multiple = TRUE),
  selectInput(inputId = "bp_gender", label = "Gender", choices = unique.genders, selected = unique.genders, multiple = TRUE),
  selectInput(inputId = "bp_income_group", label = "Income", choices = unique.income.groups, selected = unique.income.groups, multiple = TRUE),
  selectInput(inputId = "bp_region", label = "Region", choices = unique.regions, selected = unique.regions, multiple = TRUE),
  selectInput(inputId = "bp_persona", label = "Persona", choices = unique.personas, selected = unique.personas, multiple = TRUE),
  sliderInput(inputId = "bp_number_of_products", label = "Number of Top Products", min = 0, max = 20, value = 5, step = 1)
)
```

Row {data-height=800}
-------------------------------------

```{r q3_output}
renderPlot({
  brand <- mobile[get(age.group.name) %in% input$bp_age_group & get(gender.name) %in% input$bp_gender & 
                  get(income.group.name) %in% input$bp_income_group & get(region.name) %in% input$bp_region & 
                  get(persona.name) %in% input$bp_persona][, .(ave.user.friendly = mean(get(user.friendly.name), na.rm=TRUE),
                                                      ave.fast = mean(get(fast.name), na.rm=TRUE),
                                                      ave.battery.life = mean(get(battery.life.name), na.rm=TRUE),
                                                      ave.camera = mean(get(camera.name), na.rm=TRUE),
                                                      ave.sleek = mean(get(sleek.name), na.rm=TRUE),
                                                      ave.stylish = mean(get(stylish.name), na.rm=TRUE),
                                                      ave.status = mean(get(status.symbol.name), na.rm=TRUE),
                                                      ave.screen = mean(get(good.screen.size.name), na.rm=TRUE),
                                                      ave.boring = 10 - mean(get(boring.name), na.rm=TRUE),
                                                      ave.bulky = 10 - mean(get(bulky.name), na.rm=TRUE),
                                                      ave.fragile = 10 - mean(get(fragile.name), na.rm=TRUE),
                                                      ave.expensive = 10 - mean(get(expensive.name), na.rm=TRUE)), by=product.name]
  brand.overall <- brand[,.(overall.ave.perception = round.numerics(rowMeans(.SD), 2)), by=product.name]
  setorderv(x = brand.overall, cols = "overall.ave.perception", order = -1)
  top.bp <- brand.overall[1:input$bp_number_of_products]

  barplot(height = top.bp[, overall.ave.perception], names.arg = top.bp[,get(product.name)], space=0.01, las = 1, ylab = sprintf("Ovearall Brand Perception"), ylim = c(-5, 15), axes = F, col = "dodgerblue")
  axis(side = 2, at = 20*(0:5), las = 2)
  
  space_val = 0
    text(x = -0.4 + 1:top.bp[,.N] * (1+space_val), y = top.bp[, overall.ave.perception], labels = sprintf("%.1f%%", top.bp[, overall.ave.perception]), pos = 3)
})
```


Outcome Gaps
=====================================  

Row {data-height=500}
-------------------------------------

```{r q4_input}
inputPanel(
  selectInput(inputId = "outcome_engagement_state_1", label = "Select State of Engagement #1:", choices = states.of.engagement, selected = states.of.engagement[1]),
  selectInput(inputId = "outcome_engagement_state_2", label = "Select State of Engagement #2:", choices = states.of.engagement, selected = states.of.engagement[2]),
  checkboxInput(inputId = "outcome_show_percentages", label = "Show Percentages", value = TRUE),
  sliderInput(inputId = "outcome_number_of_products", label = "Number of Top Products", min = 0, max = 20, value = 5, step = 1),
  sliderInput(inputId = "outcome_digits", label = "Number of Decimal Digits", min = 0, max = 6, value = 2, step = 1)
)
```

Row {data-height=500}
-------------------------------------

```{r q4_output}
renderPlot({
   
  ## outcome 1
  if(input$outcome_engagement_state_1 == satisfaction.name){
    ave1 <- mobile[, .(ave.1 = mean(get(input$outcome_engagement_state_1), na.rm=TRUE)), by = product.name]
  }
  if(input$outcome_engagement_state_1 != satisfaction.name){
    ave1 <- mobile[!is.na(get(input$outcome_engagement_state_1)), .(ave.1 = sum(get(input$outcome_engagement_state_1) == 1) /.N ), by = product.name]
  }
  ## outcome 2
  if(input$outcome_engagement_state_2 == satisfaction.name){
    ave2 <- mobile[, .(ave.2 = mean(get(input$outcome_engagement_state_2), na.rm=TRUE)), by = product.name]
  }
  if(input$outcome_engagement_state_2 != satisfaction.name){
    ave2 <- mobile[!is.na(get(input$outcome_engagement_state_2)), .(ave.2 = sum(get(input$outcome_engagement_state_2) == 1) /.N ), by = product.name]
  }
  ## merge
  engage.diff <- merge(ave1, ave2, by= product.name)[, .(Difference = 100*(ave.1 - ave.2)), by=product.name]
  setorderv(x = engage.diff, cols = "Difference", order = -1)
  topk.outcome.gap <- engage.diff[1:input$outcome_number_of_products]

  barplot(height = topk.outcome.gap[, Difference], names.arg = topk.outcome.gap[,get(product.name)], space=0.01, las = 1, main = sprintf("%s vs %s", input$outcome_engagement_state_1, input$outcome_engagement_state_2), xlab = "Products", ylab ="Outcome Gap", ylim = c(-10, 120), axes = F, col = "dodgerblue")
  axis(side = 2, at = 20*(0:5), las = 2)
  
  if(input$outcome_show_percentages == TRUE){
    space_val = 0
    text(x = -0.4 + 1:topk.outcome.gap[ , .N] * (1+space_val), y = topk.outcome.gap[ ,Difference], labels = sprintf(paste0("%.", input$outcome_digits, "f%%"), topk.outcome.gap[ ,Difference]), pos = 3)
  }
})

```

Aggregated Engagement
=====================================  

Row {data-height=500}
-------------------------------------


```{r q5_input}

inputPanel(
  selectInput(inputId="ae_state", label = "State of Engagement:", choices = states.of.engagement, selected = states.of.engagement[1]),
  selectInput(inputId="ae_product", label = "Product", choices = unique.products, selected = unique.products[1], multiple = TRUE),
  selectInput(inputId="ae_inputs", label = "Choose Inputs:", choices = c(age.group.name, gender.name, region.name, income.group.name, persona.name, bp.traits), selected = c(age.group.name, gender.name, region.name, income.group.name), multiple = TRUE),
  selectInput(inputId="ae_age_group", label = "Age", choices = unique.age.groups, selected = unique.age.groups, multiple = TRUE),
  selectInput(inputId = "ae_gender", label = "Gender", choices = unique.genders, selected = unique.genders, multiple = TRUE),
  selectInput(inputId = "ae_income_group", label = "Income", choices = unique.income.groups, selected = unique.income.groups, multiple = TRUE),
  selectInput(inputId = "ae_region", label = "Region", choices = unique.regions, selected = unique.regions, multiple = TRUE),
  selectInput(inputId = "ae_persona", label = "Persona", choices = unique.personas, selected = unique.personas, multiple = TRUE)
)

```

Row {data-height=500}
-------------------------------------

```{r q5_output}
renderDataTable({
  ag.engage(mobile, input$ae_state, input$ae_product, input$ae_age_group, input$ae_gender, input$ae_income_group, input$ae_region, input$ae_persona)
})
```

